---
title: "Further Analyss of the NYC Data"
author: "Andrea Ramirez and Karen Britt"
date: "6/23/2021"
last modified: "06/24/2021"
output: html_document
---
First we will install the required packages for visualizations
```{r}
library (readr)
library(ggplot2)
library(tidyverse)
library(scales)
library(modelr)
library(lubridate)
theme_set(theme_bw())
options(repr.plot.width=4, repr.plot.height=3)
```


Now we will install the police complaint dataset
```{r}

```

How does the number of police complaints change throughout the year?

```{r}
#line graph of the number of complaints on the y axis and the date on the x axis (each year is a diffrent line, months on the bottom, year is on legend )  


```




### Which gender has more complaints 
gender <- nyc_clean %>% 
  group_by(gender)
  summerize(sum(gender)) %>% 
    
genger %>%
    ggplot(aes(x = gender)) + geom_bar()
    
### How many complaints does an officer average out per year
    
    
### Did Complainst Begin to be accumulated at the beggining of end of their career 
  


  
### How does the precinct/nighborhood the police work in affect the number of complaints 


  