---
title: "Further Analyss of the NYC Data"
author: "Andrea Ramirez and Karen Britt"
date: "6/23/2021"
last modified: "06/24/2021"
output: html_document
---
First we will install the required packages for visualizations
```{r}
library (readr)
library(ggplot2)
library(tidyverse)
library(scales)
library(modelr)
library(lubridate)
theme_set(theme_bw())
options(repr.plot.width=4, repr.plot.height=3)
```


Now we will install the police complaint data set
```{r}
library(readr)
complaints <- read_csv("nyc_clean.csv")

View(complaints)
```

How does the number of police complaints change throughout the year?

```{r}
# groups year and keeps only count
complaints_bydate <- complaints %>%
  distinct(IncidentDate, ComplaintID) %>%
  group_by(IncidentDate) %>%
  summarise(count = n())

View(complaints_bydate)
```
line graph of the number of complaints on the y axis and the date on the x axis (each year is a different line, months on the bottom, year is on legend )  

```{r}
#line graph of all years and complaints
ggplot(data = complaints_bydate) + 
  geom_line(mapping = aes(x = IncidentDate, y = count))
```

```{r}
# creates a year column

complaints_bydate <- complaints_bydate %>%
  separate(IncidentDate, c("year", "month", "day"))

View(complaints_bydate)
```

```{r}
#groups by year
#complaints_byyear <- complaints_bydate %>%
#  group_by(year) %>%
#  summarise(count = n())

#View(complaints_byyear)
```

```{r}
#line graph of all years and complaints
ggplot(data = complaints_bydate) + 
  geom_line(mapping = aes(x = year, y = count))
```

```{r}
# creates filters for all years besides 2005 because there was only one value

#2006 filter 
twentysix_filter <- filter(complaints_bydate, year == "2006")

#2007 filter 
twentyseven_filter <- filter(complaints_bydate, year == "2007")

#2008 filter 
twentyeight_filter <- filter(complaints_bydate, year == "2008")

#2009 filter 
twentynine_filter <- filter(complaints_bydate, year == "2009")

#2010 filter 
twentyten_filter <- filter(complaints_bydate, year == "2010")

#2011 filter 
twentyeleven_filter <- filter(complaints_bydate, year == "2011")

#2013 filter 
twentytwelve_filter <- filter(complaints_bydate, year == "2012")

#2014 filter 
twentythirteen_filter <- filter(complaints_bydate, year == "2013")

#2014 filter 
twentyfourteen_filter <- filter(complaints_bydate, year == "2014")

#2015 filter 
twentyfifteen_filter <- filter(complaints_bydate, year == "2015")

#2016 filter 
twentysixteen_filter <- filter(complaints_bydate, year == "2016")

#2017 filter 
twentyseventeen_filter <- filter(complaints_bydate, year == "2017")
```

```{r}
#line graph of complaints in 2006
ggplot(data = twentysix_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2006")

#line graph of complaints in 2007
ggplot(data = twentyseven_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2007")

#line graph of complaints in 2008
ggplot(data = twentyeight_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2008")

#line graph of complaints in 2009
ggplot(data = twentynine_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2009")

#line graph of complaints in 2010
ggplot(data = twentyten_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2010")

#line graph of complaints in 2011
ggplot(data = twentyeleven_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2011")

#line graph of complaints in 2012
ggplot(data = twentytwelve_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2012")

#line graph of complaints in 2013
ggplot(data = twentythirteen_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2013")

#line graph of complaints in 2014
ggplot(data = twentyfourteen_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2014")

#line graph of complaints in 2015
ggplot(data = twentyfifteen_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2015")

#line graph of complaints in 2016
ggplot(data = twentysixteen_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2016")

#line graph of complaints in 2017
ggplot(data = twentyseventeen_filter) + 
  geom_line(mapping = aes(x = month, y = count)) + 
  ggtitle("Number of Police Complaints each Month, NYC 2017")
```
```{r}
typeof(complaints_bydate$count)
```

```{r}
# hypothesis testing, ANOVA test of count and year

myAnovaResults <- aov(count ~
year, data = complaints_bydate)
summary(myAnovaResults)
```
```{r}
# hypothesis testing, ANOVA test of count and year

myAnovaResults <- aov(count ~
month, data = complaints_bydate)
summary(myAnovaResults)
```




Further Analysis:
Which gender has more complaints 
gender <- nyc_clean %>% 
  group_by(gender)
  summerize(sum(gender)) %>% 
    
genger %>%
    ggplot(aes(x = gender)) + geom_bar()
    
How many complaints does an officer average out per year
Did Complainst Begin to be accumulated at the beggining of end of their career 
How does the precinct/nighborhood the police work in affect the number of complaints 


  